Kindly Bent to Free Us

### 2020-06-23 kindly/extensions.tex
fixed unfortunate language about branching

Our formalization of \lang does not contain branching constructs. As a consequence,
subexpressions are always executed sequentially. Ordering is import
for the splitting relation introduced in \cref{sdtyping}, as it must
coincide with the order of evaluation. To account for borrows and linear
values in different branches, we need a different, straightforward (symmetric) join relation.
Its definition follows immediately from the semantics of borrows and linearity
shown so far and it must be used in the typing rules for branching
constructs such as if-then-else and pattern matching.
This extension is implemented in our prototype.

>>>>

Our formalization of \lang does not cover conditionals. In the
typing rules, a conditional is supported as usual by checking all
branches with the same constraint and typing environment and requiring
the return types to match.
It materializes in the inference algorithm as a straightforward
(symmetric) join relation which is used for all elimination rules on
sum types.
This extension is implemented in our prototype.
